APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-25 paper.tex
Add abstract from Sammy Chang.

\begin{abstract}
    Abstract goes here.
\end{abstract}

>>>>

\begin{abstract}
This report covers application of Linear Algebra in the Finite Element Method.
More specifically we delve into the Direct Stiffness Method (DSM) which is one
common method to apply FEM. Our code is able to solve 2D and 3D truss systems
using DSM. DSM is essentially based on three knowns: forces, displacements and
elastic modulus'. The scope of the project only covers 2D trusses, but the
code does have the ability to solve 3D systems.
\end{abstract}
